LogChunks: A Data Set for Build Log Analysis

### 2020-02-06 msr-paper/paper.tex

\textit{Benchmarking Build Log Analysis Techniques}.
\logchunks is a spin-off from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
\logchunks can be a benchmark to evaluate other build log analysis techniques.
For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
\smallskip

>>>>

\paragraph{Benchmarking Build Log Analysis Techniques}
\logchunks originated from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques. %\todo{cite journal paper (or preprint?)}.
\logchunks can be a benchmark to evaluate other build log analysis techniques.
For example, one can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves build failure reasons.
